Estimations plots

### 2024-01-26 procesamiento/03-prod_analysis-descriptives.Rmd
a

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal2,redist,
                        class3=class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,country3,region,
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  na.omit()

@@

macro_data <- df2 %>%
  group_by(country2,country3) %>%
  summarise_at(c("redist","egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
                 "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
  as.data.frame()

macro_data %>%  
ggplot(aes(y=egal2, x=homclass)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Class homogeneity")+
  ylab("Redistributive preferences") +
  labs(title = "Redistributive preferences and Class homogeneity",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$redist, use='complete.obs'),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_homo_redist.png",device = "png",
       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)

>>>>

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,
               sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  egal2,
  class3,
  homclass,
  Q03pcm,
  edyears,
  female,
  agenum,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp",
  "gini_mkt",
  d10d1,
  rgdpna,
  oecd,
  country2, country
) %>%
  mutate(logrgdpna = log(rgdpna),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2) %>%
  filter(country2 != "SVN") %>%
  na.omit()

@@

macro_data <- df2 %>%
  group_by(country2,country3) %>%
  summarise_at(c("egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
                 "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
  as.data.frame()

macro_data %>%  
ggplot(aes(y=egal2, x=homclass)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Class homogeneity")+
  ylab("Redistributive preferences") +
  labs(title = "Redistributive preferences and Class homogeneity",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$egal2, use='complete.obs'),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_homo_egal.png",device = "png",
       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)

### 2024-01-26 procesamiento/prod_analysis-plots-models.Rmd
a

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_minimal())
ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
```

@@

```{r coef-egal-fullsample}
ggplot(df_p %>% filter(depvar=="Full sample"),
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 3,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class (VI+VII)",
      "Intermediate class (III+IV+V)",
      "Class-based homogeneity"
    )
  )+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(int_homo), ", Countries=", lme4::ngrps(int_homo)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Redistributive Preferences (Index)") +
  theme(axis.text.y.left = element_text(face = "plain", size = 12))
ggsave(plot = last_plot(),filename = "coefplot-egal-fullsample.png",device = "png",
       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)

>>>>

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_bw())
ggplot2::theme_update(text=element_text(size=15,  family="serif"))  
```

@@

```{r coef-egal-fullsample}
coefplot1 <-  
df_p %>% filter(depvar=="Full sample" & group =="Full network") %>% 
  add_row(effect="fixed",group="Full network",term = "classService",depvar= "Full sample",.before = 2)

coefplot1$term <- factor(coefplot1$term,levels = rev(c("homclass","classService","class3Intermediate class (III+IV)","class3Working Class (V+VI+VII)")))

ggplot(coefplot1,
       aes(x = estimate, y = term, color = group)) +
  geom_vline(xintercept = 0) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    size = 1,
    width = 0.2,
    position = position_dodge(0.5)
  ) +
  geom_point(
    shape = 21,
    size = 5,
    fill = "white",
    position = position_dodge(0.5)
  ) +
  facet_grid(~depvar)+
  scale_y_discrete(
    labels = c(
      "Working Class",
      # str_wrap("Service Class: Intermediate class",width = 20)),
       # bquote(bold("Social Class (Ref: Service Class)") Intermediate class"),
    # "Social Class (Ref: Service Class)\n\nIntermediate class\n\n",
    "Intermediate class",
    bquote(bold("Social Class \n(Ref: Service Class)")),
    "Class-based homogeneity"
    ))+
  scale_color_discrete(guide = guide_legend(reverse = TRUE))+
  labs(
    # caption = paste0("N=", nobs(fsample_egal_full_ind), ", Countries=", lme4::ngrps(fsample_egal_full_ind)),
    color = "Model",
    x="Coefficients (fixed effects)",y=NULL,
    title = "Redistributive Preferences") +
  theme(axis.text.y.left = element_text(face = "plain", size = 15),
        legend.position="none")

ggsave(plot = last_plot(),filename = "coefplot-egal-fullsample.png",device = "png",
       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 15)
```
